Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-16 paper/main.tex
add note regarding whole-brain in intro

% open question
In this study, we investigate if increased hemodynamic activity in the PPA that
is usually detected by contrasting blocks of pictures can also be revealed under
more ecologically conditions.
% we use 2 naturalistic stimuli
To answer this question, we operationalized the perception of both visual and
auditory spatial information using two naturalistic stimuli (see
\citep{hamilton2018revolution, hasson2008neurocinematics,
sonkusare2019naturalistic} for reviews).
% AV stimulus
The operationalization of visual spatial perception is based on an annotation of cuts
and depicted locations in the audio-visual movie ``Forrest Gump'', while
% AD stimulus
non-visual spatial perception is investigated using an annotation of
spatial references in the speech occurring in the movie's audio-description.
% GLM contrasts
We applied model-based, mass-univariate analyses to a series of datasets
with BOLD fMRI data from naturalistic and conventional block-design stimulation
from the same set of participants, available from the open-data resource
\href{http://www.studyforrest.org}{studyforrest.org}
\citep{hanke2016simultaneous, hanke2014audiomovie, sengupta2016extension}.
\todo{cite Häusler \& Hanke 2021}

@@

% we checked correlations
Since we annotated events in fixed time courses, the modeled hemodynamic
time-series could be correlated leading to shared variance and thus low
detection power of subsequent analyses.
% correlations within stimuli and across stimuli
Hence, we tested for correlation of regressors across the eight segments of each
stimulus and also for correlations of regressors across both stimuli (s. Figure
\ref{fig:reg-corr})
% correlations within each stimulus
The computed Pearson correlation coefficients demonstrate no to minor
correlations of modeled hemodynamic time-series belonging to the same stimulus.
% (highest) correlations across stimuli
The highest correlations are apparent between auditory low-level confounds
across stimuli (\texttt{fg\_av\_ger\_rms} and \texttt{fg\_ad\_rms}, r=.7635;
\texttt{fg\_av\_ger\_lrdiff} and \texttt{fg\_ad\_lrdiff} and , r=.7749).
% no surprise
This was expected and served as a ``sanity check'' since the audio track of the
audio-description is the audio track of the movie but featuring the additional
narrator (s. Figure \ref{fig:reg-corr}).
% encouraged by that we build contrasts (statement)
As a result, we felt encouraged to create voxel-wise GLM $t$-contrasts similarly
to previous studies that used controlled stimuli.

@@

% intro
We tested our modeled hemodynamic responses based on stimulus annotations by
conducting standard two-level general linear model (GLM) analyses to create
subject-specific results across the 8 segments for every subject and each
stimulus.
% level 3
Subsequent, third-level analyses averaged contrast estimates over subjects.

@@

% previous studies
Previous studies reported increased hemodynamic activity in the PPA when
participants were watching static pictures of landscape compared to pictures of
faces or objects (e.g. \citep{epstein1998ppa, epstein1999parahippocampal})
whereas one study using spoken sentences reported mixed results
\citep{aziz2008modulation}.
% current study: similar
In line with previous studies, we operationalized spatial perception via general
linear model (GLM) $t$-contrasts.
% current study: dissimilar
Contrary to previous studies, our current approach is not based on carefully
designed sets of stimuli but based on annotated stimulus features incidentally
occurring in two naturalistic stimuli.
% group AV
On a group level, whole brain-analysis results for the audio-visual movie show
significantly increased hemodynamic activity spatially overlapping with a
traditionally localized PPA but also extending into earlier visual cortices.
% group AD
Results for the audio-description also reveal significant activation in the PPA
but restricted to its anterior part.
% individual level
On an individual level, results of the audio-description show significant
bilateral clusters in the anterior PPA of nine subjects and a unilateral cluster
in one subjects.
% meaning: generalization to naturalistic stimuli
Results suggest that increased activation in the PPA during the perception of
static pictures generalize to the perception of spatial information embedded in
a movie and an exclusively auditory stimulus.
% meaning: aPPA vs. pPPA
Our results provide further evidence that the PPA can be divided into functional
subregions.
% narrative as substitute
An auditory narrative might substitute a visual paradigm to localize the PPAs
anterior part in visually impaired subjects.

>>>>

% open question
In this study, we investigate if increased hemodynamic activity in the PPA that
is usually detected by contrasting blocks of pictures can also be revealed under
more ecologically conditions.
% we use 2 naturalistic stimuli
To answer this question, we operationalized the perception of both visual and
auditory spatial information using two naturalistic stimuli (see
\citep{hamilton2018revolution, hasson2008neurocinematics,
sonkusare2019naturalistic} for reviews).
% AV stimulus
The operationalization of visual spatial perception is based on an annotation of
cuts and depicted locations in the audio-visual movie ``Forrest Gump'', while
% AD stimulus
non-visual spatial perception is investigated using an annotation of spatial
references in the speech occurring in the movie's audio-description.
% GLM contrasts
We applied whole-brain, model-based, mass-univariate analyses to a series of
datasets with BOLD fMRI data from naturalistic and conventional block-design
stimulation from the same set of participants, available from the open-data
resource \href{http://www.studyforrest.org}{studyforrest.org}
\citep{hanke2016simultaneous, hanke2014audiomovie, sengupta2016extension}.
\todo{cite Häusler \& Hanke 2021}

@@

% we checked correlations
Since we annotated events in fixed time courses, the modeled hemodynamic
time-series could be correlated leading to shared variance and thus low
detection power of subsequent analyses.
% correlations within stimuli and across stimuli
Hence, we tested for correlation of regressors across the eight segments of each
stimulus and also for correlations of regressors across both stimuli (s. Figure
\ref{fig:reg-corr})
% correlations within each stimulus
The computed Pearson correlation coefficients demonstrate no to minor
correlations of modeled hemodynamic time-series belonging to the same stimulus.
% (highest) correlations across stimuli
The highest correlations are apparent between auditory low-level confounds
across stimuli (\texttt{fg\_av\_ger\_rms} and \texttt{fg\_ad\_rms}, r=.7635;
\texttt{fg\_av\_ger\_lrdiff} and \texttt{fg\_ad\_lrdiff} and , r=.7749).
% no surprise
This was expected and served as a ``sanity check'' since the audio track of the
audio-description is the audio track of the movie but featuring the additional
narrator (s. Figure \ref{fig:reg-corr}).
% encouraged by that we build contrasts (statement)
As a result, we felt encouraged to create voxel-wise general linear model (GLM)
$t$-contrasts similarly to previous studies that used controlled stimuli.

@@

% intro
We tested our modeled hemodynamic responses based on stimulus annotations by
conducting standard two-level GLM analyses to create
subject-specific results across the 8 segments for every subject and each
stimulus.
% level 3
Subsequent, third-level analyses averaged contrast estimates over subjects.

@@

% previous studies
Previous studies reported increased hemodynamic activity in the PPA when
participants were watching static pictures of landscape compared to pictures of
faces or objects (e.g. \citep{epstein1998ppa, epstein1999parahippocampal})
whereas one study using spoken sentences reported mixed results
\citep{aziz2008modulation}.
% current study: similar
In line with previous studies, we operationalized spatial perception via GLM $t$-contrasts.
% current study: dissimilar
Contrary to previous studies, our current approach is not based on carefully
designed sets of stimuli but based on annotated stimulus features incidentally
occurring in two naturalistic stimuli.
% group AV
On a group level, whole brain-analysis results for the audio-visual movie show
significantly increased hemodynamic activity spatially overlapping with a
traditionally localized PPA but also extending into earlier visual cortices.
% group AD
Results for the audio-description also reveal significant activation in the PPA
but restricted to its anterior part.
% individual level
On an individual level, results of the audio-description show significant
bilateral clusters in the anterior PPA of nine subjects and a unilateral cluster
in one subjects.
% meaning: generalization to naturalistic stimuli
Results suggest that increased activation in the PPA during the perception of
static pictures generalize to the perception of spatial information embedded in
a movie and an exclusively auditory stimulus.
% meaning: aPPA vs. pPPA
Our results provide further evidence that the PPA can be divided into functional
subregions.
% narrative as substitute
An auditory narrative might substitute a visual paradigm to localize the PPAs
anterior part in visually impaired subjects.
